### 2019-10-24 thesis/txt/3-data-set.tex
writing a lot in chapter 2, various figures, data analysis and figures in thesis

\subsection{Sampling Logs}
For each build the \texttt{TravisRequester} then selects a log to download. Logs in Travis CI are not directly attributed to \texttt{build}s, but to \texttt{job}s.
A single build can consist of multiple jobs, e.g. building and executing tests in various different testing environments.
\texttt{TravisRequester} therefore queries each build for a job, which has the same state.
A failed build can have successful job executions, as just one failed job leads to the whole build being marked as failed.
For the selected jobs, our tool then queries the Travis API V3 and obtains the respective build log.

@@

\subsection{Inter-Rater Reliability}
re-labeling of parts of the labels - cohen's kappa

\subsection{Sending Mails to Developers}
study description \& results

>>>>

\subsection{Sampling Logs}
For each build the \texttt{TravisRequester} then selects a log to download. Logs in Travis CI are not directly attributed to \texttt{build}s, but to \texttt{job}s.
A single build can consist of multiple jobs, e.g.\ building and executing tests in various different testing environments.
\texttt{TravisRequester} therefore queries each build for a job, which has the same state.
A failed build can have successful job executions, as just one failed job leads to the whole build being marked as failed.
For the selected jobs, our tool then queries the Travis API V3 and obtains the respective build log.

@@

\subsection{Inter-Rater Reliability}
re-labeling of parts of the labels - cohen's kappa
\subsubsection{Introduction}
\subsubsection{Method}
\subsubsection{Results}
\subsubsection{Discussion}
\subsubsection{Threats to Validity}

\subsection{Sending Mails to Developers}
\subsubsection{Introduction}
For the \emph{Failing Build Log Data Set} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
As we are not involved in the development of any of the open source projects within our data set we could only rely on our previous experience with differen build logs and systems.
We only looked into the logs and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.

The person who probably knows best why a build failed is the one committing the changes which triggered the build.
If the build was e.g.\ part of a pull request then developer likely looked at it and tried to fix it so the pull request could be accepted.
In this section we describe how we validate the extractions of the build failure reason the \emph{Failing Build Log Data Set} describes.
\subsubsection{Method}
Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information. 
\subsubsection{Results}
\subsubsection{Discussion}
\subsubsection{Threats to Validity}

\section{Threats to Validity}
\bp{some errors are not shown inside the log: we always choose an extraction, if we did not see the actual reason for the error reported, we chose the part stating that an error occured / the build failed

we are not developers of the projects and we did not analyze their travis configuration: possible that we labeled parts that presented an error, though the build did not fail because of that error

end all the points with: we tried to remedy this by (e.g.\ validations)
}

### 2019-10-24 thesis/txt/5-study.tex
writing a lot in chapter 2, various figures, data analysis and figures in thesis

\chapter{Technique Comparison Study}
\label{sec:study}
\section{Introduction}
running evaluation to compare the different techniques

\section{Method}
\begin{figure}[h]
	\centering
	\includegraphics[page=6, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
	\caption{Process of our technique comparison study}
	\label{fig:study}
\end{figure}
\todo{run!}

@@

\section{Results}
\todo{accuracy (or so) of retrievals with growing example number // overall averages \& detailed look on special cases //}

>>>>

\chapter{Technique Comparison Study}
\label{sec:study}
\section{Introduction}
To investigate how different factors \todo{do we list these somewhere?} influence BLIRTs we evaluate the three techniques implemented in our tool on the \emph{Failing Build Log Data Set}.

\begin{figure}[h]
	\centering
	\includegraphics[page=6, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
	\caption{Process of our technique comparison study}
	\label{fig:study}
\end{figure}

\section{Method}
We configure the technique for every example set with an increasing count of I/O examples and then run the retrieval on the next I/O example, the \emph{test I/O example}.
The output from the test I/O example is the oracle for our evaluation.
The examples are sorted and selected chronologically, i.e. the technique is configured with examples from the directly preceeding build logs to extract information from the test log.
The extraction quality of a BLIRT run is evaluated on only one build log, as it should be suitable for every coming example.
Especially the one directly succeeding the configuration.
If the information retrieval there is bad, we expect the user to directly change the configuration again or be dissapointed with his selection of technique.

When evaluating a BLIRT run we measure the following data points:
\begin{itemize}
	\item \textbf{Successful} A BLIRT run is successful when the retrieved output contains all the lines the oracle output.
	\item \textbf{Accuracy} \todo{currently: levenstein difference of input and output, maybe: change to false pos and neg lines}
	\item \textbf{Proximity} \todo{can we usefully calculate that????}
\end{itemize}

@@

\section{Results}
\todo{accuracy (or so) of retrievals with growing example number // overall averages \& detailed look on special cases //}
\begin{figure}[hp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/accuracy-success-all.pdf}
		\caption{caption}
		\label{fig:accuracy-success-all}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/line-diff-all.pdf}
		\caption{caption}
		\label{fig:line-diff-all}
	\end{minipage}
\end{figure}

\begin{figure}[hp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/ouput-failed-pbe.pdf}
		\caption{caption}
		\label{fig:ouput-failed-pbe}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-all.pdf}
		\caption{caption}
		\label{fig:success-all}
	\end{minipage}
\end{figure}

\begin{figure}[hp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-ir.pdf}
		\caption{caption}
		\label{fig:success-examples-ir}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-kw.pdf}
		\caption{caption}
		\label{fig:success-examples-kw}
	\end{minipage}
\end{figure}

\begin{figure}[hp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-pbe.pdf}
		\caption{caption}
		\label{fig:success-examples-pbe}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-pbe.pdf}
		\caption{caption}
		\label{fig:success-examples-pbe}
	\end{minipage}
\end{figure}
